Thesis: draft

### 2021-03-24 draft.tex
started writing abstract

\selectlanguage{english}
\thispagestyle{empty}
\begin{abstract}
The past decade, the rise of social media has become undeniable. More and more people are getting engaged on some type of social media platform and hence, it is probably not wrong to say that nowadays most of us have, beside our real life, a virtual life on social media. This rapidly increased engagement on social media undoubtedly has many advantages. However, every upside has a downside and social media is no different. This thesis deals with the impact of social media on the formation and evolution of opinions in society. Social media allows for the spread of information at a faster pace and at an unprecedented scale. However, people are still bounded by time- and cognitive constraints. In order to handle the information overflow, social media companies design filtering algorithms that can fine-tune and individualize the information someone is exposed to. 
% definetely not finished!! --> this will be put in summary! (think about how you want lay-out: chapter of abstract style?)
\end{abstract}

@@

\chapter*{Summary}
\addcontentsline{toc}{chapter}{Summary}

\selectlanguage{dutch}
\chapter*{Nederlandstalige samenvatting}
\addcontentsline{toc}{chapter}{Nederlandstalige samenvatting}

>>>>

@@

\selectlanguage{english}
\begin{abstract}
\addcontentsline{toc}{chapter}{Abstract}
The past decade, the rise of social media has become undeniable. More and more people are getting engaged on some type of social media platform and hence, it is probably not wrong to say that nowadays most of us have, beside our real life, a virtual life on social media. This rapidly increased engagement on social media undoubtedly has many advantages. However, every upside has a downside and social media is no different. This thesis deals with the impact of social media on the formation and evolution of opinions in society.\\ 
Social media allows for the spread of information at a faster pace and at an unprecedented scale. However, people are still bounded by time- and cognitive constraints. In order to handle the information overflow, social media companies design filtering algorithms that can fine-tune and individualize the information someone is exposed to. This filtering and individualizing of information may have some potentially dangerous downfalls in the sense that people might get trapped in "echo chambers" that confirm their own beliefs. It is important to know the effects of such algorithmic personalization on the appearance and formation of phenomena such as polarization, spread of extremism, formation of echo chambers, etc.\\
People are, however, more than sheep that thoughtlessly follow their shepherd (contrary to what some books might lead us to believe). They are capable of critical thinking and may be hesitant to change their current opinion. This aspect of potential stubbornness should not be ignored.\\
In this thesis toy models are designed to investigate the interplay between network structure, filtering algorithms and individual resistance to change in the evolution of two competing opinions. We will investigate which network properties (eg. community structure, clustering coefficient, etc) may enhance or hamper the formation of echo chambers. We will use some basic filtering algorithms to determine their possible effects on the appearance of echo chambers and we will investigate the impact of individual stubbornness. Beside that, we will also pay some attention to the possible ways of distributing the opinions; we will compare randomly distributed cases to cases where entire communities are given one single opinion.
% definetely not finished!! --> add some type of conclusions or not? talk about running model on real world networks?
\end{abstract}

\selectlanguage{dutch}
\begin{abstract}
\addcontentsline{toc}{chapter}{Samenvatting}
The past decade, the rise of social media has become undeniable. More and more people are getting engaged on some type of social media platform and hence, it is probably not wrong to say that nowadays most of us have, beside our real life, a virtual life on social media. This rapidly increased engagement on social media undoubtedly has many advantages. However, every upside has a downside and social media is no different. This thesis deals with the impact of social media on the formation and evolution of opinions in society. Social media allows for the spread of information at a faster pace and at an unprecedented scale. However, people are still bounded by time- and cognitive constraints. In order to handle the information overflow, social media companies design filtering algorithms that can fine-tune and individualize the information someone is exposed to. 
% definetely not finished!! --> this will be put in summary! (think about how you want lay-out: chapter of abstract style?)
\end{abstract}
